### 2013-08-15 proposal/proposal/chapter1.tex
Changes

\setcounter{chapter}{1}
%*******************************START INTRODUCTION **********************************
\section{Introduction}\label{sec:intro}
In this chapter we introduce the context of this research, which is about argumentation-based negotiation dialogue games. We also present the motivations behind this work and the research questions. Also, we discuss the objective of this research and our preliminary contributions. Proposal organization is presented in the last section.

\subsection{Context of the research}\label{sec:context}

@@

\subsection{Motivations and research questions}\label{sec:motivation}

@@

\subsection{Research objectives and contributions}\label{sec:contribution}

@@

\subsection{Research outline}\label{sec:outline}
The rest of the paper is organized as follows: In Section~\ref{sec:Argumentation}, we present a  brief theoretical background on the argumentation system
and agent's theory, strategic reasoning, tactic reasoning and risk of failure notions are also discussed in this section. In Section~\ref{sec:uncertainty},
we present the agent's uncertainty measures using Shannon entropy, which include type I (measuring the uncertainty of the agent about selecting the right move)
and type II (measuring the uncertainty degree that the selected move will be accepted). Argument classification is also presented in this section. Related work
is discussed in Section~\ref{sec:related}. Finally, conclusion and future work are presented in Section~\ref{sec:conclusion}.

>>>>

\setcounter{chapter}{0}
%*******************************START INTRODUCTION **********************************
\chapter{Introduction}\label{sec:intro}
In this chapter we introduce the context of this research, which is about argumentation-based negotiation dialogue games. We also present the motivations behind this work and the research questions. Also, we discuss the objective of this research and our preliminary contributions. Proposal organization is presented in the last section.

\section{Context of the research}\label{sec:context}

@@

\section{Motivations and research questions}\label{sec:motivation}

@@

\section{Research objectives and contributions}\label{sec:contribution}

@@

\section{Research outline}\label{sec:outline}
The rest of the paper is organized as follows: In Section~\ref{sec:Argumentation}, we present a  brief theoretical background on the argumentation system
and agent's theory, strategic reasoning, tactic reasoning and risk of failure notions are also discussed in this section. In Section~\ref{sec:uncertainty},
we present the agent's uncertainty measures using Shannon entropy, which include type I (measuring the uncertainty of the agent about selecting the right move)
and type II (measuring the uncertainty degree that the selected move will be accepted). Argument classification is also presented in this section. Related work
is discussed in Section~\ref{sec:related}. Finally, conclusion and future work are presented in Section~\ref{sec:conclusion}.
